Efficient implementation of penalized regression\\for genetic risk prediction

### 2018-10-02 paper/PRS.tex
submitted

\noindent$^\ast$To whom correspondence should be addressed.

@@

In conclusion, our study demonstrates that penalized logistic regression can achieve more discriminative polygenic risk scores, while being applicable to large-scale individual-level data thanks to the implementation we provide in the R package bigstatsr.\\

\textbf{Contact:} \href{florian.prive@univ-grenoble-alpes.fr}{florian.prive@univ-grenoble-alpes.fr} \& \href{michael.blum@univ-grenoble-alpes.fr}{michael.blum@univ-grenoble-alpes.fr}
}

>>>>

\noindent$^\ast$To whom correspondence should be addressed.\\

\noindent Contacts: 
\begin{itemize}
\item \url{florian.prive@univ-grenoble-alpes.fr}
\item \url{hugues.aschard@pasteur.fr}
\item \url{michael.blum@univ-grenoble-alpes.fr}
\end{itemize}

@@

In conclusion, our study demonstrates that penalized logistic regression can achieve more discriminative polygenic risk scores, while being applicable to large-scale individual-level data thanks to the implementation we provide in the R package bigstatsr.
}
